---
title: "UNM08 predictiveness in test"
output: pdf_document
date: "2024-01-18"
---

```{r setup, include=FALSE}
library(tidyverse)
library(afex)
library(BayesFactor)
library(apa)
library(emmeans)
load("UNM08_proc_data.RData")
# function to force scientific formatting of numbers (used for large BFs)
changeSciNot <- function(n) {
  output <- format(n, scientific = TRUE, digits = 2) #Transforms the number into scientific notation even if small
  output <- sub("e", "x10^", output) #Replace e with 10^
  output <- sub("\\+0?", "", output) #Remove + symbol and leading zeros on exponent, if > 1
  output <- sub("-0?", "-", output) #Leaves - symbol but removes leading zeros on exponent, if < 1
  output <- paste0(output,"^")
  # output = strsplit(output, "^", fixed = TRUE)
  # output = paste0(output[[1]][1],"^", output[[1]][2], "^")
  output
}

# function to extract and report BFs with error %s
report_BF_and_error <- function(BF_in, sci_not = TRUE, hyp = "alt"){
  
  if (hyp == "alt") {
    BF_notation = "BF~10~ = "
  } else if (hyp == "null") {
    BF_notation = "BF~01~ = "
  }
  
  if (sci_not == TRUE) {
    BF_value = changeSciNot(extractBF(BF_in)$bf) # change to sci notation
  } else {
    BF_value = round(extractBF(BF_in)$bf,2) # otherwise round
  }
  
  paste0(BF_notation, 
         BF_value, 
         " &plusmn; ", 
         round(100*extractBF(BF_in)$error,2), 
         "%")
}

```
```{r, include=FALSE}
#Create probable response variable, as we are using the uncertain condition
stage1 <- stage1 %>%
  mutate(prob_response = case_when((cue1 == 1 | cue1 == 3) & response == "o1_image" ~ 1,
                                   (cue1 == 1 | cue1 == 3) & response == "o2_image" ~ 0, 
                                   (cue1 == 2 | cue1 == 4) & response == "o1_image" ~ 0,
                                   (cue1 == 2 | cue1 == 4) & response == "o2_image" ~ 1))
stage2 <- stage2 %>%
  mutate(prob_response = case_when((cue1 == 1 | cue1 == 3) & response == "o1_image" ~ 1,
                                   (cue1 == 1 | cue1 == 3) & response == "o2_image" ~ 0, 
                                   (cue1 == 2 | cue1 == 4) & response == "o1_image" ~ 0,
                                   (cue1 == 2 | cue1 == 4) & response == "o2_image" ~ 1))
#some exclusion criteria
block6 <- filter(stage1, block == 6) %>%
  group_by(pNum, condition) %>%
  summarise (mean_response = mean(prob_response, na.rm = TRUE))

low_acc <- filter(block6, mean_response < 0.6) 
low_acc <- low_acc$pNum

stage1 <- filter(stage1, !pNum %in% not_passed_pNum & !pNum %in% low_acc)
stage2 <- filter(stage2, !pNum %in% not_passed_pNum & !pNum %in% low_acc)
test <- filter(test, !pNum %in% not_passed_pNum & !pNum %in% low_acc)


N <- unique(stage1$pNum)
```
``` {r, include = FALSE}
test <- test %>%
  mutate(trial_type = case_when((target == 1 & distractor == 2) | (target == 2 & distractor == 1) ~ "Pt vs Pf",
                                (target == 5 & distractor == 6) | (target == 6 & distractor == 5) ~ "NPt vs NPf",
                                (target == 1 & (distractor == 5 | distractor == 6)) | (target == 2 & (distractor == 5 | distractor == 6)) ~ "Pt vs NPf",
                                (target == 5 & (distractor == 1 | distractor == 2)) | (target == 6 & (distractor == 1 | distractor == 2)) ~ "NPt vs Pf",
                                (target == 3 & distractor == 4) | (target == 4 & distractor == 3) ~ "Pt vs Pf",
                                (target == 7 & distractor == 8) | (target == 8 & distractor == 7) ~ "NPt vs NPf",
                                (target == 3 & (distractor == 7 | distractor == 8)) | (target == 4 & (distractor == 7 | distractor == 8)) ~ "Pt vs NPf",
                                (target == 7 & (distractor == 3 | distractor == 4)) | (target == 8 & (distractor == 3 | distractor == 4)) ~ "NPt vs Pf"),
         predictiveness = case_when(trial_type == "Pt vs Pf" ~ "predictive",
                                    trial_type == "NPt vs NPf"  ~ "non-predictive",
                                    trial_type == "Pt vs NPf" ~ "predictive",
                                    trial_type == "NPt vs Pf" ~ "non-predictive"),
         congruence = case_when(trial_type == "Pt vs Pf" ~ "congruent",
                                    trial_type == "NPt vs NPf"  ~ "congruent",
                                    trial_type == "Pt vs NPf" ~ "incongruent",
                                    trial_type == "NPt vs Pf" ~ "incongruent"))
```


### Accuracy

```{r, include = FALSE}
MA_test <- test %>%
  group_by(trial_type, condition) %>%
  summarise(mean_acc = mean(acc, na.rm = TRUE),
            sd_acc = sd(acc, na.rm = TRUE)/sqrt(length(acc)))
```
```{r, echo = FALSE}
ggplot(MA_test) +
  geom_col(mapping = aes(x = condition, y = mean_acc, fill = trial_type), position = position_dodge2()) +
  geom_errorbar(aes(x= condition, y = mean_acc, ymin = mean_acc-sd_acc, ymax = mean_acc+sd_acc, group = trial_type), color = "black", width=.2,position=position_dodge(0.9)) +
  scale_x_discrete(name = "Type of cue") +
  scale_y_continuous(name="Accuracy") +
  labs(title = "Mean accuracy in the test phase")+
  scale_fill_brewer(palette = "PRGn")
```

```{r, include=FALSE}
#ANOVA
acc_test <- test %>%
  group_by (pNum, condition, predictiveness, congruence) %>%
  summarise(mean_acc = mean(acc, na.rm = TRUE))
acc_test$pNum <- factor(acc_test$pNum)
acc_test$condition <- factor(acc_test$condition)
acc_test$predictiveness <- factor(acc_test$predictiveness)
acc_test$congruence <- factor(acc_test$congruence)
ANOVA_acc_test <- aov_car(formula = mean_acc ~ condition + Error(pNum/predictiveness*congruence), data = acc_test)
print(ANOVA_acc_test)

bay_ANOVA_acc_test <- anovaBF(formula = mean_acc ~ condition + predictiveness +congruence + pNum,
        data = data.frame(acc_test),
        whichRandom = "pNum")
print(bay_ANOVA_acc_test)
bay_ANOVA_acc_test_condxp <- bay_ANOVA_acc_test[4]/bay_ANOVA_acc_test[3]
print(bay_ANOVA_acc_test_condxp)
bay_ANOVA_acc_test_pxcong <- bay_ANOVA_acc_test[13]/bay_ANOVA_acc_test[7]
print(bay_ANOVA_acc_test_pxcong)
bay_ANOVA_acc_test_condxcong <- bay_ANOVA_acc_test[10]/bay_ANOVA_acc_test[6]
print(bay_ANOVA_acc_test_condxcong)
bay_ANOVA_acc_test_condxpxcong <- bay_ANOVA_acc_test[18]/bay_ANOVA_acc_test[17]
print(bay_ANOVA_acc_test_condxpxcong)
```
```{r, include = FALSE}
# Pairwise comparisons between group levels
#condition analysis
acc_test_pxcong_int <- emmeans(ANOVA_acc_test, ~ congruence|predictiveness)
pairs(acc_test_pxcong_int, adjust = "bon")
```
A mixed methods ANOVA found a significant the main effect of the Condition (`r apa(ANOVA_acc_test, effect = "condition")`, `r report_BF_and_error(bay_ANOVA_acc_test[1])`), that showed moderate bayesian evidence for the alternative hypothesis, of the Predictiveness (`r apa(ANOVA_acc_test, effect = "predictiveness")`, `r report_BF_and_error(bay_ANOVA_acc_test[2])`), showing strong alternative evidence, and the effect of the PredictivenessxCongruence interaction (`r apa(ANOVA_acc_test, effect = "predictiveness:congruence")`, `r report_BF_and_error(bay_ANOVA_acc_test_pxcong[1])`), with very strong alternative evidence. Bonferroni corrected pairwise comparisons showed significant differences between the congruent and incongruent trials both when the targets were non-predictive (*T*(87) = 2.911, *p* = .005) and when they were predictive (*T*(87) = 2.492, *p* = .015). There rest of effects were not significant(Congruence: `r apa(ANOVA_acc_test, effect = "congruence")`, `r report_BF_and_error(bay_ANOVA_acc_test[5])`, ConditionxPredictiveness: `r apa(ANOVA_acc_test, effect = "condition:predictiveness")`, `r report_BF_and_error(bay_ANOVA_acc_test_condxp[1])`; ConditionxCongruence: `r apa(ANOVA_acc_test, effect = "condition:predictiveness:congruence")`, `r report_BF_and_error(bay_ANOVA_acc_test_condxpxcong[1])`; ConditionxPredictivenessxCongruence: `r apa(ANOVA_acc_test, effect = "predictiveness:congruence")`, `r report_BF_and_error(bay_ANOVA_acc_test_pxcong[1])`). All these effects showed moderate bayesian evidence for the null hypothesis, except for the ConditionxCongruence interaction, that showed strong null evidence.

### Corrected memory score (hits x1, errors x0)

```{r, include = FALSE}
Mc_mem_test <- test %>%
  group_by(trial_type, condition) %>%
  summarise(mean_c_mem = mean(c_mem_score, na.rm = TRUE),
            sd_c_mem = sd(c_mem_score, na.rm = TRUE)/sqrt(length(c_mem_score)))
```
```{r, echo = FALSE}
ggplot(Mc_mem_test) +
  geom_col(mapping = aes(x = condition, y = mean_c_mem, fill = trial_type), position = position_dodge2()) +
  geom_errorbar(aes(x= condition, y = mean_c_mem, ymin = mean_c_mem-sd_c_mem, ymax = mean_c_mem+sd_c_mem, group = trial_type), color = "black", width=.2,position=position_dodge(0.9)) +
  scale_x_discrete(name = "Type of cue") +
  scale_y_continuous(name="Corrected memory score") +
  labs(title = "Mean corrected memory score in the test phase")+
  scale_fill_brewer(palette = "PRGn")
```
```{r, include=FALSE}
#ANOVA
c_mem_test <- test %>%
  group_by (pNum, condition, predictiveness, congruence) %>%
  summarise(mean_c_mem = mean(c_mem_score, na.rm = TRUE))
c_mem_test$pNum <- factor(c_mem_test$pNum)
c_mem_test$condition <- factor(c_mem_test$condition)
c_mem_test$predictiveness <- factor(c_mem_test$predictiveness)
c_mem_test$congruence <- factor(c_mem_test$congruence)
ANOVA_c_mem_test <- aov_car(formula = mean_c_mem ~ condition + Error(pNum/predictiveness*congruence), data = c_mem_test)
print(ANOVA_c_mem_test)

bay_ANOVA_c_mem_test <- anovaBF(formula = mean_c_mem ~ condition + predictiveness + congruence + pNum,
        data = data.frame(c_mem_test),
        whichRandom = "pNum")
print(bay_ANOVA_c_mem_test)
bay_ANOVA_c_mem_test_condxp <- bay_ANOVA_c_mem_test[4]/bay_ANOVA_c_mem_test[3]
print(bay_ANOVA_c_mem_test_condxp)
bay_ANOVA_c_mem_test_pxcong <- bay_ANOVA_c_mem_test[13]/bay_ANOVA_c_mem_test[7]
print(bay_ANOVA_c_mem_test_pxcong)
bay_ANOVA_c_mem_test_condxcong <- bay_ANOVA_c_mem_test[10]/bay_ANOVA_c_mem_test[6]
print(bay_ANOVA_c_mem_test_condxcong)
bay_ANOVA_c_mem_test_condxpxcong <- bay_ANOVA_c_mem_test[18]/bay_ANOVA_c_mem_test[17]
print(bay_ANOVA_c_mem_test_condxpxcong)
```
```{r, include = FALSE}
# Pairwise comparisons between group levels
c_mem_test_cond <- emmeans(ANOVA_c_mem_test, ~ condition)
pairs(c_mem_test_cond, adjust = "bon")
c_mem_test_pxcong_int <- emmeans(ANOVA_c_mem_test, ~ congruence|predictiveness)
pairs(c_mem_test_pxcong_int, adjust = "bon")
```
A mixed methods ANOVA found a significant the main effect of the Condition (`r apa(ANOVA_c_mem_test, effect = "condition")`, `r report_BF_and_error(bay_ANOVA_c_mem_test[1])`), that showed anecdotal bayesian evidence for the alternative hypothesis, of the Predictiveness (`r apa(ANOVA_c_mem_test, effect = "predictiveness")`, `r report_BF_and_error(bay_ANOVA_c_mem_test[2])`), showing extreme alternative evidence, and the effect of the PredictivenessxCongruence interaction (`r apa(ANOVA_c_mem_test, effect = "predictiveness:congruence")`, `r report_BF_and_error(bay_ANOVA_c_mem_test_pxcong[1])`), with very strong alternative evidence. Bonferroni corrected pairwise comparisons showed significant differences between the congruent and incongruent trials both when the targets were non-predictive (*T*(87) = 2.966, *p* = .004) and when they were predictive (*T*(87) = 2.492, *p* = .013). There rest of effects were not significant (Congruence: `r apa(ANOVA_c_mem_test, effect = "congruence")`, `r report_BF_and_error(bay_ANOVA_c_mem_test[5])`; ConditionxPredictiveness: `r apa(ANOVA_c_mem_test, effect = "condition:predictiveness")`, `r report_BF_and_error(bay_ANOVA_c_mem_test_condxp[1])`; ConditionxCongruence: `r apa(ANOVA_c_mem_test, effect = "condition:predictiveness:congruence")`, `r report_BF_and_error(bay_ANOVA_c_mem_test_condxpxcong[1])`; ConditionxPredictivenessxCongruence: `r apa(ANOVA_c_mem_test, effect = "predictiveness:congruence")`, `r report_BF_and_error(bay_ANOVA_c_mem_test_pxcong[1])`). Bayesian evidence was moderate for the null hypothesis for the main effect of Congruence and the 3 way interaction, anecdotal evidence for the ConditionxPredictiveness and strong for the ConditionxCongruence interaction.

## Test without the certain_short condition

### Accuracy
```{r, include = FALSE}
test_2g <- filter(test, condition == "Certain Long" | condition == "Uncertain")
```
```{r, include = FALSE}
MA_test_2g <- test_2g %>%
  group_by(trial_type, condition) %>%
  summarise(mean_acc = mean(acc, na.rm = TRUE),
            sd_acc = sd(acc, na.rm = TRUE)/sqrt(length(acc)))
```
```{r, echo = FALSE}
ggplot(MA_test_2g) +
  geom_col(mapping = aes(x = condition, y = mean_acc, fill = trial_type), position = position_dodge2()) +
  geom_errorbar(aes(x= condition, y = mean_acc, ymin = mean_acc-sd_acc, ymax = mean_acc+sd_acc, group = trial_type), color = "black", width=.2,position=position_dodge(0.9)) +
  scale_x_discrete(name = "Type of cue") +
  scale_y_continuous(name="Accuracy") +
  labs(title = "Mean accuracy in the test phase")+
  scale_fill_brewer(palette = "PRGn")
```
```{r, include=FALSE}
#ANOVA
acc_test_2g <- test_2g %>%
  group_by (pNum, condition, predictiveness, congruence) %>%
  summarise(mean_acc = mean(acc, na.rm = TRUE))
acc_test_2g$pNum <- factor(acc_test_2g$pNum)
acc_test_2g$condition <- factor(acc_test_2g$condition)
acc_test_2g$predictiveness <- factor(acc_test_2g$predictiveness)
acc_test_2g$congruence <- factor(acc_test_2g$congruence)
ANOVA_acc_test_2g <- aov_car(formula = mean_acc ~ condition + Error(pNum/predictiveness*congruence), data = acc_test_2g)
print(ANOVA_acc_test_2g)

bay_ANOVA_acc_test_2g <- anovaBF(formula = mean_acc ~ condition + predictiveness + congruence + pNum,
        data = data.frame(acc_test_2g),
        whichRandom = "pNum")
print(bay_ANOVA_acc_test_2g)
bay_ANOVA_acc_test_2g_condxp <- bay_ANOVA_acc_test_2g[4]/bay_ANOVA_acc_test_2g[3]
print(bay_ANOVA_acc_test_2g_condxp)
bay_ANOVA_acc_test_2g_pxcong <- bay_ANOVA_acc_test_2g[13]/bay_ANOVA_acc_test_2g[7]
print(bay_ANOVA_acc_test_2g_pxcong)
bay_ANOVA_acc_test_2g_condxcong <- bay_ANOVA_acc_test_2g[10]/bay_ANOVA_acc_test_2g[6]
print(bay_ANOVA_acc_test_2g_condxcong)
bay_ANOVA_acc_test_2g_condxpxcong <- bay_ANOVA_acc_test_2g[18]/bay_ANOVA_acc_test_2g[17]
print(bay_ANOVA_acc_test_2g_condxpxcong)
```
A mixed methods ANOVA found a significant the main effect of the Condition (`r apa(ANOVA_acc_test_2g, effect = "condition")`, `r report_BF_and_error(bay_ANOVA_acc_test_2g[1])`), that showed moderate bayesian evidence for the alternative hypothesis, and of the Predictiveness (`r apa(ANOVA_acc_test_2g, effect = "predictiveness")`, `r report_BF_and_error(bay_ANOVA_acc_test_2g[2])`), showing anecdotal alternative evidence. It is worth noting that both the ConditionxPredictiveness and PredictivenessxCongruence interactions were marginally significant (ConditionxPredictiveness: `r apa(ANOVA_acc_test_2g, effect = "condition:predictiveness")`, `r report_BF_and_error(bay_ANOVA_acc_test_2g_condxp[1])`; PredictivenessxCongruence: `r apa(ANOVA_acc_test_2g, effect = "predictiveness:congruence")`, `r report_BF_and_error(bay_ANOVA_acc_test_2g_pxcong[1])`), the first showing anecdotal null bayesian evidence and the latter showing anecdotal alternative evidence. There rest of effects were not significant (Congruence: `r apa(ANOVA_acc_test_2g, effect = "congruence")`, `r report_BF_and_error(bay_ANOVA_acc_test_2g[5])`; ConditionxCongruence: `r apa(ANOVA_acc_test_2g, effect = "condition:predictiveness:congruence")`, `r report_BF_and_error(bay_ANOVA_acc_test_2g_condxpxcong[1])`; ConditionxPredictivenessxCongruence: `r apa(ANOVA_acc_test_2g, effect = "predictiveness:congruence")`, `r report_BF_and_error(bay_ANOVA_acc_test_2g_pxcong[1])`), all showing moderate null bayesian evidence. 

### Corrected memory score (hits x1, errors x0)

```{r, include = FALSE}
Mc_test_2g <- test_2g %>%
  group_by(trial_type, condition) %>%
  summarise(mean_mem = mean(c_mem_score, na.rm = TRUE),
            sd_mem = sd(c_mem_score, na.rm = TRUE)/sqrt(length(c_mem_score)))
```
```{r, echo = FALSE}
ggplot(Mc_test_2g) +
  geom_col(mapping = aes(x = condition, y = mean_mem, fill = trial_type), position = position_dodge2()) +
  geom_errorbar(aes(x= condition, y = mean_mem, ymin = mean_mem-sd_mem, ymax = mean_mem+sd_mem, group = trial_type), color = "black", width=.2,position=position_dodge(0.9)) +
  scale_x_discrete(name = "Type of cue") +
  scale_y_continuous(name="Memory score") +
  labs(title = "Mean memory score in the test phase")+
  scale_fill_brewer(palette = "PRGn")
```
```{r, include=FALSE}
#ANOVA
mem_test_2g <- test_2g %>%
  group_by (pNum, condition, predictiveness, congruence) %>%
  summarise(mean_mem = mean(c_mem_score, na.rm = TRUE))
mem_test_2g$pNum <- factor(mem_test_2g$pNum)
mem_test_2g$condition <- factor(mem_test_2g$condition)
mem_test_2g$predictiveness <- factor(mem_test_2g$predictiveness)
mem_test_2g$congruence <- factor(mem_test_2g$congruence)
ANOVA_mem_test_2g <- aov_car(formula = mean_mem ~ condition + Error(pNum/predictiveness*congruence), data = mem_test_2g)
print(ANOVA_mem_test_2g)

bay_ANOVA_mem_test_2g <- anovaBF(formula = mean_mem ~ condition + predictiveness + congruence + pNum,
        data = data.frame(mem_test_2g),
        whichRandom = "pNum")
print(bay_ANOVA_mem_test_2g)
bay_ANOVA_mem_test_2g_condxp <- bay_ANOVA_mem_test_2g[4]/bay_ANOVA_mem_test_2g[3]
print(bay_ANOVA_mem_test_2g_condxp)
bay_ANOVA_mem_test_2g_pxcong <- bay_ANOVA_mem_test_2g[13]/bay_ANOVA_mem_test_2g[7]
print(bay_ANOVA_mem_test_2g_pxcong)
bay_ANOVA_mem_test_2g_condxcong <- bay_ANOVA_mem_test_2g[10]/bay_ANOVA_mem_test_2g[6]
print(bay_ANOVA_mem_test_2g_condxcong)
bay_ANOVA_mem_test_2g_condxpxcong <- bay_ANOVA_mem_test_2g[18]/bay_ANOVA_mem_test_2g[17]
print(bay_ANOVA_mem_test_2g_condxpxcong)
```
```{r, include = FALSE}
# Pairwise comparisons between group levels
#condition analysis
#mem_test_2g_condition <- emmeans(ANOVA_mem_test_2g, ~ condition)
#pairs(mem_test_2g_condition, adjust = "bon")
```
A mixed methods ANOVA found a significant the main effect of the Condition (`r apa(ANOVA_mem_test_2g, effect = "condition")`, `r report_BF_and_error(bay_ANOVA_mem_test_2g[1])`), that showed anecdotal bayesian evidence for the alternative hypothesis, of the Predictiveness (`r apa(ANOVA_mem_test_2g, effect = "predictiveness")`, `r report_BF_and_error(bay_ANOVA_mem_test_2g[2])`), showing very strong alternative evidence, and the ConditionxPredictiveness (`r apa(ANOVA_mem_test_2g, effect = "condition:predictiveness")`, `r report_BF_and_error(bay_ANOVA_mem_test_2g_condxp[1])`), also showing anecdotal evidence. It is worth noting that the PredictivenessxCongruence interaction was marginally significant (`r apa(ANOVA_mem_test_2g, effect = "predictiveness:congruence")`, `r report_BF_and_error(bay_ANOVA_mem_test_2g_pxcong[1])`), showing anecdotal alternative evidence. There rest of effects were not significant (Congruence: `r apa(ANOVA_mem_test_2g, effect = "congruence")`, `r report_BF_and_error(bay_ANOVA_mem_test_2g[5])`; ConditionxCongruence: `r apa(ANOVA_mem_test_2g, effect = "condition:predictiveness:congruence")`, `r report_BF_and_error(bay_ANOVA_mem_test_2g_condxpxcong[1])`; ConditionxPredictivenessxCongruence: `r apa(ANOVA_mem_test_2g, effect = "predictiveness:congruence")`, `r report_BF_and_error(bay_ANOVA_mem_test_2g_pxcong[1])`), all showing moderate null bayesian evidence. 